---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Shrisha Yelluru"
date: "2/28/2019"
output: html_document
toc: true
toc_depth: 3
number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#### Can you name which package is associated with each task below?

Plotting -gglot2  
Data munging/wrangling -dplyr  
Reshaping (speading and gathering) data - tidyr  
Importing/exporting data -readr  

#### Now can you name two functions that you’ve used from each package that you listed above for these tasks?

Plotting -ggplot2  
ggplot(), aes(), geom_area(), geom_boxplot(), xlab(), ylab()

Data munging/wrangling -dplyr..  
mutate(), select(), filter(), summarise(), arrange()

Reshaping data -tidyr  
gather()  
spred()  

Importing/exporting data -readr  
read_csv(), read_file(), write_file



#### Fix this code with the fewest number of changes possible so it works:
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
```
#### Fix this code so it works:
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
```

#### Look at the code below and comment on what happened to the values in the vector.
#### Answer : 
```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
## [1] "1" "2" "3" "4" "5"
```

#### Download the rail_trail.txt file from Canvas (in the Midterm Exam section) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.

```{r echo=FALSE}
library(tidyverse)
file_path <- '/Users/syelluru/Documents/Shrisha/compscix-415-2-assignments/Mid_Term/Whickham.csv'
csv_data <- read_csv(file = file_path)
view(csv_data)
```
#### Export the file into a comma-separated file and name it “rail_trail.csv”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.

```{r echo=FALSE}

write_delim(csv_data, delim = ',', path = '/Users/syelluru/Documents/Shrisha/compscix-415-2-assignments/Mid_Term/rail_trail.csv')
file_path <- '/Users/syelluru/Documents/Shrisha/compscix-415-2-assignments/Mid_Term/rail_trail.csv'
csv_data <- read_csv(file = file_path)
view(csv_data)
```

#### Critique this graphic: give only three examples of what is wrong with this graphic. Be concise.
1. The YES and NO count DO NOT add upto 100%
2. Differentiation of AGE and SEX should be in separate graph.
3. NOT all gender orientation data is NOT presented.

#### Reproduce this graphic using the diamonds data set.
```{r}
library(ggplot2)
a <- ggplot(diamonds, aes(cut, carat)) +  
  geom_boxplot() + 
  xlab("CARAT OF DIAMOND") + ylab("CUT OF DIAMOND")
a + coord_flip()
```

#### The previous graphic is not very useful. We can make it much more useful by changing one thing about it. Make the change and plot it again.

```{r}
a <- ggplot(diamonds, aes(cut, carat, fill=color)) +  
  geom_boxplot() + 
  xlab("CARAT OF DIAMOND") + ylab("CUT OF DIAMOND")
a + coord_flip()
```

#### 1. Is this data “tidy”? If yes, leave it alone and go to the next problem. If no, make it tidy. Note: this data set is called table2 and is available in the tidyverse package. It should be ready for you to use after you’ve loaded the tidyverse package.

```{r, echo=FALSE}
table2 %>%
    spread(key = type, value = count)
```

#### 2. Create a new column in the diamonds data set called price_per_carat that shows the price of each diamond per carat (hint: divide). Only show me the code, not the output.
```{r}
mutate(diamonds,
  price_per_carat = price/carat)
```

#### 3. For each cut of diamond in the diamonds data set, how many diamonds, and what proportion, have a price > 10000 and a carat < 1.5? There are several ways to get to an answer, but your solution must use the data wrangling verbs from the tidyverse in order to get credit.
```{r}
my_subset <- nrow(subset(diamonds, price >= 10000 & carat < 1.5))
orig <- nrow(diamonds)
(my_subset/orig)*100.0
# 1.55% of the data
```
#### Do the results make sense? Why?
#### Do we need to be wary of any of these numbers? Why?


### EDA
Take a look at the txhousing data set that is included with the ggplot2 package and answer these questions:
view(txhousing)

#### 1.During what time period is this data from? The data is from 2000 to 2015
```{r, echo=FALSE}
min(txhousing$year, na.rm=T)
max(txhousing$year, na.rm=T)
```
#### 2.How many cities are represented? 46 cities are presented.
```{r}
distinct(txhousing, city)
```
#### 3.Which city, month and year had the highest number of sales?
#### Answer : Huston in July 2015 had highest, 8945 sales.
```{r}
arrange(txhousing, desc(sales))
```
#### 4.What kind of relationship do you think exists between the number of listings and the number of sales? Check your assumption and show your work.
```{r}
ggplot(txhousing, aes(listings, sales)) +  
  geom_boxplot()
```

#### 5.What proportion of sales is missing for each city?

```{r}
txhousing %>% group_by(city)
```

### 6.Looking at only the cities and months with greater than 500 sales:

```{r}
my_subset <- nrow(subset(txhousing, sales >= 500))
orig <- nrow(txhousing)
(my_subset/orig)*100.0
```
#### 6.1 Are the distributions of the median sales price (column name median), when grouped by city, different? The same? Show your work.
```{r}
```

#### 6.2 Any cities that stand out that you’d want to investigate further?
```{r}
```

#### 6.3 Why might we want to filter out all cities and months with sales less than 500?
```{r}
```

