---
title: "COMPSCIX 415.2 Homework 9/Final"
author: "Shrisha Yelluru"
date: "4/1/2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# COMPSCIX 415.2 Homework 9/Final

1## Excercise 1 - Sampling Distributions, Functions and For Loops

Loading necessary libraries.

```{r libraries}
library(tidyverse)
library(broom)
library(dplyr)
```

Sample code used to create exponential distribution.

```{r sample}
# sample size
samp_size <- 100
# set the rate parameter
samp_rate <- 1/10000
# take sample
rexp(n = samp_size, rate = samp_rate)
rexp
```

### Step 1

Creating an exponential distribution using samp_size as input parameter for the function.

```{r}
samp_fun <- function(samp_size, samp_rate) {
  
  exp_dist <- rexp(n = samp_size, rate = samp_rate)
  
  # Calculating mean of the sample
  samp_avg <- mean(exp_dist)
  
  # Calculating standard deviation of the sample
  samp_std_dev <- sd(exp_dist)
  
  stats <- list(samp_avg = samp_avg, samp_std_dev = samp_std_dev)
  return(stats)
}

output_1 = samp_fun(100, 1/10000)
output_1
```


### Step 2

Running the above function 1000 times using a for loop.

```{r}
sample_means <- c()
sample_sds <- c()
for (i in 1:1000)
{
   output_2 <- samp_fun(50, 1/10000)
   
   sample_means <- append(sample_means, output_2$samp_avg)
   sample_sds <- append(sample_sds, output_2$samp_std_dev)
}

# Mean of the vector
sample_means

# Standard deviation of the vector
sample_sds
```

### Step 3

Plot sample means as a histogram
```{r}
hist1 <-  hist(sample_means)
```


Output of the standard deviation of the sample means
```{r}
std_sample_means <- sd(sample_means)   
std_sample_means
```

Output of the theoretical standard error
```{r}
theo_standard_error <- 10000/sqrt(50)
theo_standard_error
```

Output of the mean of the sample standard deviations
```{r}
mean_std_deviations <- mean(sample_sds)
mean_std_deviations
```

### Step 4
Repeat steps 2 and 3 with a sample size of 5000
```{r}
sample_means_step4 <- c()
sample_sds_step4 <- c()

for (i in 1:1000)
{
  output_4 <- samp_fun(5000, 1/10000)
  
  sample_means_step4 <- append(sample_means_step4, output_4$samp_avg)
  sample_sds_step4 <- append(sample_sds_step4, output_4$samp_std_dev)
}

#1
hist4 <-  hist(sample_means_step4)
hist4
```

```{r}
#2
std_sample_means_step4 <- sd(sample_means_step4)   
std_sample_means_step4

#3
theo_standard_error_step4 <- 10000/sqrt(5000)
theo_standard_error_step4

#4 
mean_std_deviations_step4 <- mean(sample_sds_step4)
mean_std_deviations_step4

emp_standard_error_step4 <- mean_std_deviations_step4/sqrt(5000)
emp_standard_error_step4

```


## Excercise 2 - Linear Regression

### Step 1
Load the data, and train build a LM 
```{r}
train <- read.csv('/Users/syelluru/Documents/Shrisha/compscix-415-2-assignments/Final/train.csv')
model <- lm(SalePrice ~ LotArea + OverallQual + ExterQual, data = train)
model
```

Using the broom package, get the coefficients and the r-sq
```{r}
coefficients <- tidy(model)
coefficients
```

```{r}
r_sq_values <- glance(model)
r_sq_values
```

### Step 2

The LotArea has a +ve intercept of 1.453 which means that the price increases by $1 for every 1.453 sqft

### Step 3
ExterQualGD -- ??

### Step 4 
```{r}
previous_model <- lm(SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = train)
previous_r_sq_values <- glance(previous_model)
previous_r_sq_values
# This model is way better. Compare with 'r_sq_values' and write theory around it that R-Squared is better
```

The previous model is better as the R-Sq value is higher.

## Excercise 3 - AB Test
```{r}
ab_test_data = read.csv('ab_test_data.csv')
ab_test_data
```

### Step 1
```{r}
proportions = ab_test_data %>% group_by(version, conversion) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
proportions
```

```{r}
freqTable = table(ab_test_data)
freqTable
prop.test(freqTable)
```